systemfit: A Package to Estimate\\ Simultaneous Equation Systems in \proglang{R}

### 2006-08-29 paper/trunk/systemfit_other.tex
all "\hat"s are "\widehat"s now
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@685 591db2bd-e0a0-4d22-8c19-2192dbb7da31

The $F$ statistic for systems of equations is
\begin{equation}
F = \frac{
   ( R \hat{\beta} - q )'
   ( R ( X' ( \hat{\Sigma} \otimes I )^{-1} X )^{-1} R' )^{-1}
   ( R \hat{\beta} - q ) /
   j
}{
   \hat{u}' ( \widehat{\Sigma} \otimes I )^{-1} \hat{u} /
   ( M \cdot T - K )
}
\end{equation}
where $j$ is the number of restrictions,
$M$ is the number of equations,
$T$ is the number of observations per equation,
$K$ is the total number of estimated coefficients, and
$\hat{\Sigma}$ is the estimated residual covariance matrix
used in the estimation.
Under the null hypothesis, $F$ has an $F$ distribution
with $j$ and $M \cdot T - K$ degrees of freedom
\citep[p.\ 314]{theil71}.

The Wald statistic for systems of equations is
\begin{equation}
W =
   ( R \hat{\beta} - q )'
   ( R \widehat{Cov} [ \hat{\beta} ] R' )^{-1}
   ( R \hat{\beta} - q )
\end{equation}
Asymptotically, $W$ has a $\chi^2$
distribution with $j$ degrees of freedom
under the null hypothesis
\citep[p.\ 347]{greene03}.

The LR statistic for systems of equations is
\begin{equation}
LR = T \cdot \left(
   log \left| \hat{ \Sigma }_r \right|
   - log \left| \hat{ \Sigma }_u \right|
   \right)
\end{equation}
where $T$ is the number of observations per equation, and 
$\hat{\Sigma}_r$ and $\hat{\Sigma}_u$ are
the residual covariance matrices calculated by formula (\ref{eq:rcov0})
of the restricted and unrestricted estimation, respectively.
Asymptotically, $LR$ has a $\chi^2$
distribution with $j$ degrees of freedom
under the null hypothesis
\citep[p.\ 349]{greene03}.

@@

\citet{hausman78} developed a test for misspecification.
The null hypothesis of the test is that all exogenous variables are
uncorrelated with all disturbance terms.
Under this hypothesis both the 2SLS and the 3SLS estimator are consistent
but only the 3SLS estimator is (asymptotically) efficient.
Under the alternative hypothesis the 2SLS estimator is consistent
but the 3SLS estimator is inconsistent.
The Hausman test statistic is,
\begin{equation}
  m = \left( \hat{\beta}_{2SLS} - \hat{\beta}_{3SLS} \right)^{'}
      \left( \Cov \left[ \hat{\beta}_{2SLS} \right] -
             \Cov \left[ \hat{\beta}_{3SLS} \right] \right)
      \left( \hat{\beta}_{2SLS} - \hat{\beta}_{3SLS} \right)
\label{eq:hausman}
\end{equation}
where $\hat{\beta}_{2SLS}$ and $\Cov \left[ \hat{\beta}_{2SLS} \right]$ are the estimated
coefficient and covariance matrix from 2SLS estimation, and
$\hat{\beta}_{3SLS}$ and $\Cov \left[ \hat{\beta}_{3SLS} \right]$ are the estimated
coefficients and covariance matrix from 3SLS estimation.
Under the null hypothesis this test statistic has a
$\chi^2$ distribution with degrees of freedom equal to the number of
estimated parameters.

>>>>

The $F$ statistic for systems of equations is
\begin{equation}
F = \frac{
   ( R \widehat{\beta} - q )'
   ( R ( X' ( \widehat{\Sigma} \otimes I )^{-1} X )^{-1} R' )^{-1}
   ( R \widehat{\beta} - q ) /
   j
}{
   \widehat{u}' ( \widehat{\Sigma} \otimes I )^{-1} \widehat{u} /
   ( M \cdot T - K )
}
\end{equation}
where $j$ is the number of restrictions,
$M$ is the number of equations,
$T$ is the number of observations per equation,
$K$ is the total number of estimated coefficients, and
$\widehat{\Sigma}$ is the estimated residual covariance matrix
used in the estimation.
Under the null hypothesis, $F$ has an $F$ distribution
with $j$ and $M \cdot T - K$ degrees of freedom
\citep[p.\ 314]{theil71}.

The Wald statistic for systems of equations is
\begin{equation}
W =
   ( R \widehat{\beta} - q )'
   ( R \widehat{Cov} [ \widehat{\beta} ] R' )^{-1}
   ( R \widehat{\beta} - q )
\end{equation}
Asymptotically, $W$ has a $\chi^2$
distribution with $j$ degrees of freedom
under the null hypothesis
\citep[p.\ 347]{greene03}.

The LR statistic for systems of equations is
\begin{equation}
LR = T \cdot \left(
   log \left| \widehat{ \Sigma }_r \right|
   - log \left| \widehat{ \Sigma }_u \right|
   \right)
\end{equation}
where $T$ is the number of observations per equation, and 
$\widehat{\Sigma}_r$ and $\widehat{\Sigma}_u$ are
the residual covariance matrices calculated by formula (\ref{eq:rcov0})
of the restricted and unrestricted estimation, respectively.
Asymptotically, $LR$ has a $\chi^2$
distribution with $j$ degrees of freedom
under the null hypothesis
\citep[p.\ 349]{greene03}.

@@

\citet{hausman78} developed a test for misspecification.
The null hypothesis of the test is that all exogenous variables are
uncorrelated with all disturbance terms.
Under this hypothesis both the 2SLS and the 3SLS estimator are consistent
but only the 3SLS estimator is (asymptotically) efficient.
Under the alternative hypothesis the 2SLS estimator is consistent
but the 3SLS estimator is inconsistent.
The Hausman test statistic is,
\begin{equation}
  m = \left( \widehat{\beta}_{2SLS} - \widehat{\beta}_{3SLS} \right)^{'}
      \left( \Cov \left[ \widehat{\beta}_{2SLS} \right] -
             \Cov \left[ \widehat{\beta}_{3SLS} \right] \right)
      \left( \widehat{\beta}_{2SLS} - \widehat{\beta}_{3SLS} \right)
\label{eq:hausman}
\end{equation}
where $\widehat{\beta}_{2SLS}$ and $\Cov \left[ \widehat{\beta}_{2SLS} \right]$ are the estimated
coefficient and covariance matrix from 2SLS estimation, and
$\widehat{\beta}_{3SLS}$ and $\Cov \left[ \widehat{\beta}_{3SLS} \right]$ are the estimated
coefficients and covariance matrix from 3SLS estimation.
Under the null hypothesis this test statistic has a
$\chi^2$ distribution with degrees of freedom equal to the number of
estimated parameters.
